Data Prep

### 2024-02-06 scripts/00.0_dataPrep.qmd
investigating the results of downsampling

>>>>

# Let's make sure the downsampling actually worked
testseason <- downsampled_10min[[1]]
with_ints <- testseason %>%
  group_by(Nili_id, dateOnly) %>%
  arrange(timestamp, .by_group = T) %>%
  mutate(int = difftime(lead(timestamp), timestamp, units = "mins"))
with_ints %>% 
  select(Nili_id, dateOnly, timestamp, int) %>%
  ggplot(aes(x = as.numeric(int), col = Nili_id))+
  geom_density()+
  theme_minimal()+
  theme(legend.position = "none") # Good, none of them are less than 0.

# Do we have any less than 10 minutes?
with_ints %>% filter(as.numeric(int) < 10) # yes, there are a lot that are less than 10 minutes

# What about less than 9 minutes?
with_ints %>% filter(as.numeric(int) < 9) # okay, so something in my code is not working to filter out the really short intervals. What's happening here?

# Oh... the way I did it actually guarantees this to happen. I cut the times into groups and then took the first one for each group. So if the first one for the previous group happened to be at the end of that group and then the first one of the next group happened to be at the beginning of that group, we can end up with arbitrarily small time intervals.

# Now, I kind of don't care, since the main point here was just to get rid of the points. But I wonder if there's a different way to do this.
```
